Spike-and-Slab LASSO Generalized Additive Models and Scalable Algorithms for High-Dimensional Data Analysis

### 2022-05-15 Manuscript/R&R/01-reviewer_1.Rmd

__Response__: Thank you for the comment. The purpose of mentioning the other several priors in the previous manuscript is to describe the generalization of the proposed algorithms. In the updated manuscript, we move the subsection describing the other priors to the supporting information so that the readers can focus on understanding the proposed scalable model. We included an additional sentence in the discussion section (see P10 "Moreover, the proposed model can easily generalize to other families of priors and smoothing functions if desired.").

@@

__Response__: We thank the reviewer for the comments. For prediction purposes, the proposed model can be flexibly used in the high-dimensional data analysis without any checking or testing. The two-part spike-and-slab LASSO prior automatically detects if the underlying signal is linear or complex. When the signal is linear, the smoothing function of the predictor only includes the linear part; when the signal is complex, cubic splines (implemented in the package) are used to estimate the complex signal. As supporting evidence, our added simulation demonstrates the proposed model predicts as good as, if not better than, the linear LASSO model, even when signals are linear and sparse (see the response to Comment 1).

>>>>

__Response__: Thank you for the comment. The purpose of mentioning several other priors in the previous manuscript is to describe the generalization of the proposed algorithms. In the updated manuscript, we move the subsection describing the other priors to the supporting information so that the readers can focus on understanding the proposed scalable model. We included an additional sentence in the discussion section (see P10 "Moreover, the proposed model can easily accommodate other families of priors and smoothing functions if desired.").

@@

__Response__: We thank the reviewer for the comments. For prediction purposes, the proposed model can be flexibly used in the high-dimensional data analysis without any checking or testing. The two-part spike-and-slab LASSO prior automatically detects if the underlying signal is linear or complex. When the signal is linear, the smoothing function of the predictor only includes the linear part; when the signal is complex, cubic splines (implemented in the package) are used to estimate the complex signal. As supporting evidence, our added simulation demonstrates that the proposed model predicts as good as, if not better than, the linear LASSO model, even when signals are linear and sparse (see the response to Comment 1).

### 2022-05-15 Manuscript/R&R/02-reviewer_2.Rmd

__Response__: We thank the reviewer for the comment. The purpose of the reparameterization step is to factor the smoothing penalty matrix in the design matrix, such that the smoothing penalty can be addressed implicitly. This contrasts to some previous methods that do not consider smoothing penalty at all. With the reparameterization, the smoothing penalty changes from $\lambda \bs \beta^T \bs S \bs \beta$ to $\lambda \bs {\beta^*}^T \bs {\beta^*}$, where the $\bs \beta$ and $\bs \beta^*$ are the coefficients of the smoothing function before and after the reparameterization respectively. However, the smoothing parameter $\lambda$, equivalently the scale parameter $s$ in the proposed model, needs to be estimated/tuned. The proposed two-part spike-and-slab LASSO prior provides the the estimation of the smoothing parameter: when the nonlinear effect does not exists, a large shrinkage is applied to the coefficients via the spike density such that coefficients shrink to 0s; when then nonlinear exists, a small shrinkage is applied via the slab density such that the smoothing function can be estimated appropriately. Moreover, the local adaptivity of he spike-and-slab LASSO prior allows the shrinkage to adapt to the data, compared to previous methods that impose an uniform shrinkage.

We clarified the utility of the reparameterization step and emphasized how the smoothness of the additive function are appropriately modeled (see P3).

@@

__Response__: Compared to other priors, the spike-and-slab double exponential prior provides three advantages. First of all, the spike-and-slab double exponential prior provides a locally adaptive shrinkage when estimating the coefficients. Hence, the smoothing functions can be estimated more accurately. Secondly, the spike-and-slab exponential prior encourages a sparse solution, making variable selection straight forward. Thirdly, the spike-and-slab double exponential prior motivates a scalable algorithm, the EM-CD algorithm, for model fitting, and hence is more feasible for high-dimensional data analysis.

@@

__Response__: We thank the reviewer for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$, in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by effect hierarchy discussed in Chipman (2004). Now, the inclusion of the nonlinear effects is dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function of $\gamma^*$ and requires minimum change of the proposed algorithms. The updated model still shows performance advantages as before.

>>>>

__Response__: We thank the reviewer for the comment. The purpose of the reparameterization step is to factor the smoothing penalty matrix in the design matrix, such that the smoothing penalty can be addressed implicitly. This contrasts with some previous methods that do not consider smoothing penalties at all. With the reparameterization, the smoothing penalty changes from $\lambda \bs \beta^T \bs S \bs \beta$ to $\lambda \bs {\beta^*}^T \bs {\beta^*}$, where the $\bs \beta$ and $\bs \beta^*$ are the coefficients of the smoothing function before and after the reparameterization respectively. However, the smoothing parameter $\lambda$, equivalently the scale parameter $s$ in the proposed model, needs to be estimated/tuned. The proposed two-part spike-and-slab LASSO prior provides the estimation of the smoothing parameter: when the nonlinear effect does not exist, a large shrinkage is applied to the coefficients via the spike density such that coefficients shrink to 0s; when then nonlinear exists, a small shrinkage is applied via the slab density such that the smoothing function can be estimated appropriately. Moreover, the local adaptivity of the spike-and-slab LASSO prior allows the shrinkage to adapt to the data, compared to previous methods that impose a uniform shrinkage.

We clarified the utility of the reparameterization step and emphasized how the smoothness of the additive function is appropriately modeled (see P3).

@@

__Response__: Compared to other priors, the spike-and-slab double exponential prior provides three advantages. First of all, the spike-and-slab double exponential prior provides a locally adaptive shrinkage when estimating the coefficients. Hence, the smoothing functions can be estimated more accurately. Secondly, the spike-and-slab exponential prior encourages a sparse solution, making variable selection straightforward. Thirdly, the spike-and-slab double exponential prior motivates a scalable algorithm, the EM-CD algorithm, for model fitting, and hence is more feasible for high-dimensional data analysis.

@@

__Response__: We thank the reviewer for the comment. We changed the prior distribution of the non-linear effects inclusion indicator to be $\gamma^\tp|\gamma, \theta \sim Bin(1, \gamma\theta)$, in comparison to $\gamma^\tp| \theta \sim Bin(1, \theta)$ previously. This prior formulation is motivated by the effect hierarchy discussed in Chipman (2004). Now, the inclusion of the nonlinear effects is dependent on the inclusion of the linear effects, and hence, reflects the hierarchy of bi-level selection. The modification of the prior doesn't complicate the model fitting algorithm. The $\gamma$ can be analytically integrated out of the density function of $\gamma^*$ and requires a minimum change of the proposed algorithms. The updated model still shows performance advantages as before.
